Empirical Evaluation of eval in R

### 2020-08-28 inst/analysis/analysis_stable.Rmd
Bette rplot

```{r subsample_for_ast}
ast_sizes <- eval_calls %>% slice_sample(n=10000) %>% mutate(expr_resolved_nodes = map_int(expr_resolved, expr_size_str))
# Now precomputed during the tracing
#ast_sizes <- read_fst(NODE_COUNT_FILE)
```

@@

ast_sizes %>%
  ggplot(aes(x = dataset, y = expr_resolved_nodes, fill = dataset, weight = nb_ev_calls)) +
  geom_violin(trim = FALSE, width=.5)+
  #geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

```{r group_expr_resolved_functions}
group_expr_resolved_functions <- expr_resolved_call_arg %>%
                            mutate(function_expr2 = groupify_function(expr_resolved_function)) %>%
                            mutate(group_function_expr = fct_collapse(function_expr2, 
                              assignment = c("<-", "[[<-", "[<-", "$<-", "<<-", "=", "@<-"),
                              slot_access = c("[", "[[", "$", "slot", "@", "::", ":::"),
                              parsing = c("parse", "str2lang", "str2expression", "parse_only", "base::parse"),
                              defusing = c("quote", "substitute", "bquote", "expr", "quo", "enquo", expression),
                              expressions = c("as.list", "as.name", "as.expression", "list", "c", "as.data.frame", "as.character", "{", "modify_lang"),
                              calling = c("call", "as.call", "do.call"),
                              environment = c("environment", "as.environment"),
                              logical = c("!", "&", "|", "&&", "||"),
                              relation = c("<", ">", "is.element", "<=", "=>", "!="),
                              choice = c("if"),
                              anonymous = c("anonymous"),
                              primitive = c("primitive"),
                              function_meta = c("sys.calls", "function", "body", "missing"),
                              arithmetic = c("+", "-", "*", "/", "%%", "^"),
                              formula = c("~", "deriv", "D", "model.frame", "rootftfunc", "contest.lmerModLmerTest", "JacFunc", "gamlss.family", "contest1D.lmerModLmerTest", "contestMD.lmerModLmerTest", "reexpr"),                           
                              other_level = "other" ))
```

@@

Another interesting figure is the degreee of polymorphism of the `expr` argument: how many different types (for `expr_resolved`) are there for one call sites?

r("nb monomorphic", nb_monomorphic)
r("percent monomorphic", ratio(nb_monomorphic, nb_call_sites))
```

```{r polymorphism}
expr_resolved_polymorphism %>% ggplot() +
  geom_bar(aes(x = polym_degree)) +
  scale_x_continuous(breaks=c(0, 1, 5, 10)) +
  labs(title = "Degree of polymorphism", x = "degree", y = "n")

@@

>>>>

```{r subsample_for_ast}
#ast_sizes <- eval_calls %>% slice_sample(n=10000) %>% mutate(expr_resolved_nodes = map_int(expr_resolved, expr_size_str))
# Now precomputed during the tracing
ast_sizes <- read_fst(path(RUN_DIR, "package-evals-traced.3/summarized-ast-size.fst")) %>% as_tibble() %>% 
      filter(eval_source_type != "<undefined>") %>%
      rename(dataset = eval_source_type) 
```

@@

ast_sizes %>%
  ggplot(aes(x = dataset, y = expr_resolved_nodes, fill = dataset, weight = nb_ev_calls), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=.5)+
  geom_boxplot(width=.05) +
  scale_y_log10(labels = scales::comma) +
  labs(y="AST size (log)") +
  theme(
     legend.position=c(0.2, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

```{r group_expr_resolved_functions}
group_expr_resolved_functions <- expr_resolved_call_arg %>%
                            mutate(function_expr2 = groupify_function(expr_resolved_function)) %>%
                            mutate(group_function_expr = fct_collapse(function_expr2, 
                              assignment = c("<-", "[[<-", "[<-", "$<-", "<<-", "=", "@<-"),
                              slot_access = c("[", "[[", "$", "slot", "@", "::", ":::"),
                              parsing = c("parse", "str2lang", "str2expression", "parse_only", "base::parse"),
                              defusing = c("quote", "substitute", "bquote", "expr", "quo", "enquo", "expression", "as.name", "as.expression"),
                              expressions = c("as.list",  "list", "c", "as.data.frame", "as.character", "{", "modify_lang"),
                              calling = c("call", "as.call", "do.call"),
                              environment = c("environment", "as.environment"),
                              logical = c("!", "&", "|", "&&", "||"),
                              relation = c("<", ">", "is.element", "<=", "=>", "!="),
                              choice = c("if"),
                              anonymous = c("anonymous"),
                              primitive = c("primitive"),
                              function_meta = c("sys.calls", "function", "body", "missing"),
                              arithmetic = c("+", "-", "*", "/", "%%", "^"),
                              formula = c("~", "deriv", "D", "model.frame", "rootftfunc", "contest.lmerModLmerTest", "JacFunc", "gamlss.family", "contest1D.lmerModLmerTest", "contestMD.lmerModLmerTest", "reexpr"),                           
                              other_level = "other" ))
```

@@

@@

Another interesting figure is the degree of consistency of the `expr` argument: how many different types (for `expr_resolved`) are there for one call sites?

r("nb monomorphic", nb_monomorphic)
r("percent monomorphic", ratio(nb_monomorphic, nb_call_sites))

nb
```

```{r polymorphism}
expr_resolved_polymorphism %>% ggplot() +
  geom_bar(aes(x = polym_degree)) +
  scale_x_continuous(breaks=c(0, 1, 5, 10)) +
  labs( x = "Number of different types", y = "n")
